---
title: "pml-xyz2009ee"
output: html_document
---


First of all, the training and testing data sets have to be preprocessed. Variables that have more than 80% missing values will not be used in either training or testing data sets.This is due to the reason that with too much missing, it will not be reliable to be used in the models. 

There are 6 unique users in this data set and we will set up user-specific models. The reason to build seperate model for each user is the homogeneity for the same user.

The generalized linear model with variable selection (Elastic Net) is used for modeling and we use the R package "glmnet". The cross validation in the glmnet package is 10 fold cross validation. The GLM with elastic net will do the modeling for clustering as well as variable selection. For example, for user carlitos, only variables "raw_timestamp_part_1", "num_window","pitch_belt","gyros_belt_z","accel_belt_x","accel_belt_z","total_accel_dumbbell"and "accel_forearm_x" are selected into the model. 
The fitting accuracies for the different users are specified as following:  98.1% for carlitos, 95.8% for petro, 93.8% for adelmo, 95.8% for charles, 95.0% for eurico, 94.7% for jeremy. Therefore, the in sample error is 1.9% for carlitos, 4,2% for for petro, 6.2% for adelmo, 4.2% for charles, 5.0% for eurico and 5.3% for jeremy. The out of sample is always greater than in sample error, therefore we have the lower bound for the out of sample error. In addition, by applying the inequality $P(|E_{in}-E_{out}|<\epsilon)<= 4(2N)^{d_{vc}}e^{-\frac{1}{8}\epsilon^{2}N}$, we can also estimate an upper bound for the out of sample error with certain probablity $\epsilon$. Here $E_{in}$ and $E_{out}$ denotes in sample and out of sample error respectively. $d_{vc}$ denotes VC dimension and N is the sample size.   

```{r}



```



```{r, echo=FALSE}

```

